%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
  {Senior Infrastructure engineer} % Job title
  {Wish Inc.} % Organization
  {} % Location
  {2022/11 - 2023/8} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Leveraged the Kubernetes Operator Pattern: implemented a controller to manage Kafka topic provisioning by using crossplane/provider-template.}
      \item {Kubernetes Cluster Management on AWS: Upgraded EKS(Amazon Elastic Kubernetes Service) from version 1.21 to 1.24 with Blue-green upgrade strategy without causing any downtime.}
      \item {Container Runtime Migration: Migrated Kubernetes container runtime from Docker to Containerd to align with industry standards.}
      \item {Container Storage Interface Migration: Migrated Kubernetes from in-tree storage plugins to Container Storage Interface (CSI) drivers and ensuring the smooth transition for end-users. }
      \item {Contribute to internal developer platform: streamlining workflows and automating processes with argocd, crossplane and OAM(kubevela), resulting in faster development cycles and increased business impact}
    \end{cvitems}
  }

  
%---------------------------------------------------------
  \cventry
    {Kubernetes Admin \& PaaS engineer} % Job title
    {Paypal Inc.} % Organization
    {} % Location
    {2020/6 - 2022/10} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Leveraged the Kubernetes Operator pattern: implemented a controller to manage Elastic Load Balancers in PayPal's private data centers for Kubernetes clusters,enhancing provisioning efficiency and resilience. }
        \item {Kubernetes Bootstrapping \& Scaling: Designed and executed a specialized tool for bootstrapping and scaling Kubernetes, tailored specifically to the network and security specifications of FinTech systems. }
        \item {SSO Integration \& Deployment: Spearheaded the integration of Single Sign-On (SSO) capabilities from its inception, further broadening its application across the entire platform, enhancing security and user experience. }
        \item {Alerting System Integration: Seamlessly integrated both Prometheus and Zabbix to establish a robust alerting mechanism, ensuring real-time monitoring and rapid issue resolution. }
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Devops engineer \& Kubernetes Admin} % Job title
    {eBay Inc. \tiny{(via outsourcing)}} % Organization
    {} % Location
    {2018/7 - 2020/5} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Kubernetes Cluster Management on Azure: Led the deployment, optimization, and secure management of Kubernetes clusters on Azure VMs, ensuring consistent uptime, peak performance, and seamless upgrades.}
        \item {Rancher Deployment: Successfully deployed Rancher for organizational use and extended its capabilities to customers, simplifying the management and scaling of containerized applications.}
        \item {Real-time Monitoring Solutions: Designed and implemented monitoring infrastructures using Prometheus, delivering real-time insights into cluster performance and significantly expediting troubleshooting efforts.        }
        \item {CI/CD Integrations: Pioneered the architecture and deployment of Jenkins-based CI/CD pipelines, accommodating daily updates and agile weekly releases in response to evolving business needs.        }
        \item {Cluster Automation: Authored advanced automation scripts in Shell, Python, and Ansible, streamlining cluster management and minimizing the need for manual oversight.        }
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {full stack engineer } % Job title
    {eBay Inc. \tiny{(via outsourcing)}} % Organization
    {} % Location
    {2016/3 - 2018/6} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {API Gateway Implementation: Created a Node.js-based API gateway that smoothly integrated new backend services while preserving the legacy system. Implemented metrics for valuable business insights.}
        \item {User Experience Enhancement: Revamped the website using ReactJS and Redux, resulting in a 30\% decrease in user-reported issues and improved user satisfaction.  }
        \item {Cross-Team Collaboration: Established effective communication channels between American teams to ensure global standards alignment.    }
        \item {Quality Assurance: Conducted regular code reviews, reducing post-deployment bugs by 10\% and maintaining coding consistency.    }
        \item {Technical Documentation: Authored comprehensive technical documentation to enhance inter-team collaboration.    }
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
  {junior java engineer } % Job title
  {Ericsson Inc. \tiny{(via outsourcing)}} % Organization
  {} % Location
  {2014/5 - 2016/3} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {End-to-End Development Contribution: Actively participated in the complete software development life cycle, from demand analysis to design and documentation. }
      \item {Agile Development: Successfully delivered a series of system improvements using the Scrum methodology. }
      \item {Efficient Software Delivery: Adopted continuous integration practices, leading to improved software quality and faster release times.    }
      \item {Quality Assurance Tools: Aided in the development of advanced testing tools and simulators, ensuring a higher standard of product reliability.  }
      \item {Technical Documentation: Authored and maintained detailed technical documents, including UML-based design proposals and user guides.     }
    \end{cvitems}
  }

%---------------------------------------------------------
\cventry
  {junior java engineer } % Job title
  {Tata Consultancy Services (TCS)} % Organization
  {} % Location
  {2012/5 - 2014/4} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Online Quoting Tool: Key contributor to the development of a quick quote tool for bank brokers' websites, enabling customers to receive online indicative quotes with ease. }
      \item {Advanced Functionality: Developed the core calculation layer within an MVC pattern tailored to specific insurance business requirements, resulting in more efficient data processing.}
      \item {Quality Assurance \& Documentation: Spearheaded the creation of project documents, work quality records, and ensured software quality by isolating and resolving defects through rigorous testing phases.  }
      \item {Database Modeling: Constructed persistent entities aligned with the business model, streamlining data storage and retrieval processes. }
    \end{cvitems}
  }

%---------------------------------------------------------
\end{cventries}
